---
title: "asdasdasd"
author: "Gyumin Lee"
date: '2021 5 5 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center', message = FALSE)
library(knitr)
library(ggplot2)
library(cowplot)
library(reshape)
```


## 4.7

### a
We first sample theta, and sigma^2 in such process:
first, get samples  from sigma^2
and then get sample from theta|sigma^2

```{r}
N = 5000
sigma2.mc = 1 / rgamma(N, 10, 2.5)
theta.mc = rnorm(N, 4.1, sigma2.mc / 20)
```

sample the mixture distribution:
```{r}
sigma.mc = sqrt(sigma2.mc)
ynew.mc = 0.31 * rnorm(N, theta.mc, sigma.mc) +
  0.46 * rnorm(N, 2 * theta.mc, 2 * sigma.mc) +
  0.23 * rnorm(N, 3 * theta.mc, 3 * sigma.mc)
qplot(ynew.mc, stat = 'hist')
```

### b
```{r}
quantile(ynew.mc, c(.125, .875))
```

### c

```{r}
# 1) Compute and normalize density
dens = density(ynew.mc)
dens.ynorm = dens$y / sum(dens$y)
# 2) Sort in decreasing order
dens.ynorm.desc = dens.ynorm[order(dens.ynorm, decreasing = TRUE)]
# 3) Find first probability value s.t. cumsum of sorted values > 0.75
cutoff = dens.ynorm.desc[min(which(cumsum(dens.ynorm.desc) > 0.75))]
in.hdp = dens.ynorm > cutoff
ggplot(data.frame(y = dens$x, density = dens.ynorm, hdp = in.hdp)) +
  geom_point(aes(x = y, y = density, color = hdp))
dens$x[c(min(which(in.hdp)), max(which(in.hdp)))]
```

Since the distribution is nearly symmetric and normally
distributed, the HDP and quantile confidence intervals are quite similar.

### d

Perhaps a combination of multiple parts of a vegetable which have known distributions (e.g. stem, fruit, leaves, etc)
